A Large-Scale Study of the Use of Eval in R

### 2020-08-25 inst/paper/main.tex
Add glue to the paste functions

This corresponds to strings loaded from a file or to metaprogramming, \ie building new variables or functions by concatenating strings together, as in Listing~\ref{code:parsepaste}. To detect this kind of metaprogramming, we look at the usage of the main concatenating functions in R, \c{paste}, \c{paste0} and \c{str_c}, and \PasteParsedEvals of the evals and \PasteParsedCallSite of the call sites using a parse function actually call a concatenating function.

>>>>

This corresponds to strings loaded from a file or to metaprogramming, \ie building new variables or functions by concatenating strings together, as in Listing~\ref{code:parsepaste}. To detect this kind of metaprogramming, we look at the usage of the main concatenating functions in R, \c{paste}, \c{paste0}, \c{glue} and \c{str_c}, and \PasteParsedEvals of the evals and \PasteParsedCallSite of the call sites using a parse function actually call a concatenating function.
